Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/relatedwork.tex
fix merge conflicts (correctly, i hope) and references in related work

Perhaps the closest work to ours is algorithm for ``data
specialization'' given by Knoblock and Ruf~\cite{knoblock96}.  As our
work, Knoblock and Ruf are concerned about the problem of splitting an
explicitly staged program into two stages.  However, they only
consider, simple first-order language and straight-line
programs. Automatic pass seperation has also been a topic of interest
in programming systems for computer graphics, where, to achieve
high-performance, programs are typically manually separated into
components by frequency of execution (Seperation into a pre-determined
set of per-frequency modules is \emph{required} by the execution model
of modern graphics architectures.)  The software engineering
challenges modifying multiple per-stage programs have led to
suggestions of writing graphics programs in an explicitly staged
programming language\,\cite{Proudfoot:2001,Foley:2011,He:2014}, and
deferring the task of pass seperation to the compiler. However, all
prior efforts, like that of Knock and Ruf\,\cite{knoblock96} have been
limited to simple, imperitive languages.

>>>>

Perhaps the closest work to ours is algorithm for ``data
specialization'' given by Knoblock and Ruf~\cite{knoblock96}.  As our
work, Knoblock and Ruf are concerned about the problem of splitting an
explicitly staged program into two stages.  However, they only
consider, simple first-order language and straight-line
programs. Automatic pass seperation has also been a topic of interest
in programming systems for computer graphics, where, to achieve
high-performance, programs are typically manually separated into
components by frequency of execution (Seperation into a pre-determined
set of per-frequency modules is \emph{required} by the execution model
of modern graphics architectures.)  The software engineering
challenges modifying multiple per-stage programs have led to
suggestions of writing graphics programs in an explicitly staged
programming language\,\cite{Proudfoot:2001,Foley:2011,He:2014}, and
deferring the task of pass seperation to the compiler. However, all
prior efforts, like that of Knock and Ruf\,\cite{knoblock96} have been
limited to simple, imperative languages.

\paragraph{Memoization.} Leaves code structure unchanged.

\paragraph{Incremental computation.} Usually not applicable within a
computation, require ``mutator'' ``core'' behavior.
